01 - TreehopperFitness: Defining strategies and calculating frequencies

### 2023-08-23 scripts/Publilia-02-strats.Rmd
init `Manuscript_runfile.Rmd` to collect all code to stats, sample sizes, figures, tables for the manuscript in a minimal reproducible script
Consolidated construction of `strats_data` for `Publilia-02-strats.Rmd` and moved that code to `Publilia-02-qc.Rmd`. Resolves https://github.com/micahpf/PubliliaFitness/issues/3#issuecomment-1676152818

clutch_status_guarding_summary_v2
```{r}
All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))

strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
```

@@

# 2 - When were females visited on their first clutch?
First I need to know when females were visited on their first clutch.
I also need to estimate the hatch date for clutches that never hatched so I can still show and run stats for relative desertion date. I do this by adding 20 days to the initiation date. The mean interval from initiation to hatch is 20 days.
```{r}
visited_1st_4d_data <- strats_data %>%
  group_by(location) %>%
    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
  ungroup() %>%
  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
                                      "Visited", "Not visited"),
         ants = ifelse(ants_removed, "Ants removed", "Control"),
         est_hatch = as_date(ifelse(is.na(hatch_date),
                                 initiation_date + 20,
                                 hatch_date)),
         est_rel2h = visit_ends-est_hatch)

@@

I also need to know how to pick just one initiator when two (or more) females are present on a clutch on the first day eggs are observed.
```{r}
visited_1st_4d_data_tb <- visited_1st_4d_data %>%
  # 1) Longest initiator
  mutate(initL = init_first_dur_rank == 1) %>% 
  # 2) Shortest initiator
  #  i) break ties by picking marked females over unmarked
  group_by(location, init_first_dur_shortest) %>% 
    mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
  ungroup() %>%
  #  ii) finally picking at random (only one case, identical predictor vars)
  group_by(location, init_first_dur_shortest, initS_tmp) %>%
    mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
  ungroup()
```

@@

## 3.1 - Ant counts on plant; some ants_removed clutches were visited by ants, and vice versa
```{r}
ant_counts <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch) %>%
    summarize(ants_removed=first(ants_removed),
              females_removed=first(females_removed),
              n_antsP=sum(ants_P,na.rm=T),
              ever_antsP=n_antsP>0,
              mean_antsP=mean(ants_P,na.rm=T),
              med_antsP=median(ants_P,na.rm=T),

              n_antsP_b4h=sum(ants_P&b4h),
              ever_antsP_b4h=n_antsP_b4h>0,
              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),

              n_antsP_afh=sum(ants_P&afh),
              ever_antsP_afh=n_antsP_afh>0,
              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

@@

## 3.2 - Ant arrival times
```{r}
antP_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsP_afh=ants_P&afh) %>%
    filter(is_antsP_afh) %>%
    slice_head(n=1) %>% 
  mutate(antP_arrival_afh=Date-est_hatch) %>%
  select(location, antP_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antP_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsP_bfh=ants_P&b4h) %>%
    filter(is_antsP_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antP_last_b4h=Date-est_hatch) %>%
  select(location, antP_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsL_afh=ants_L&afh) %>%
    filter(is_antsL_afh) %>%
    slice_head(n=1) %>% 
  mutate(antL_arrival_afh=Date-est_hatch) %>%
  select(location, antL_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsL_bfh=ants_L&b4h) %>%
    filter(is_antsL_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antL_last_b4h=Date-est_hatch) %>%
  select(location, antL_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

ant_data <- ant_counts %>%
  left_join(antP_last_b4h_data) %>%
  left_join(antP_arrival_afh_data) %>%
  left_join(antL_last_b4h_data) %>%
  left_join(antL_arrival_afh_data)

visited_1st_4d_data_ants <- visited_1st_4d_data %>%
  left_join(ant_data)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_last_b4h, color=females_removed)) +
  geom_point() +
  geom_abline(slope=1)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_arrival_afh, color=females_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  geom_abline(slope=1)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_last_b4h)) +
  geom_boxplot()

visited_1st_4d_data_ants %>%
  filter(ants=="Control") %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)

visited_1st_4d_data_ants %>%
  filter(ants=="Control", !females_removed) %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)
```

@@

### Not visited early
```{r}
## Not visited early
# ever ants b4h
ggplot(data = filter(visited_1st_4d_data_ants, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(visited_1st_4d_data_ants, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)
```

### Visited early
```{r}
# ever ants b4h
ggplot(data = filter(visited_1st_4d_data_ants,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(visited_1st_4d_data_ants,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)
```

@@

## 4.3 - Dealing with non-independence of multi-initiators: Using only longest or shortest initiator
Sample sizes
```{r}
# Samples sizes for "not visited" are the same across longests and shortests
filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL) %>% nrow()

filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initS) %>% nrow()

# Shortests have more females than longests for some reason??
filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL) %>% nrow()

filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initS) %>% nrow()

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1) %>% nrow() # 34
visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1) %>% nrow() # 36

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed) %>% nrow() # 13

visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed) %>% nrow() # 12

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1) %>% nrow() # 12

visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1) %>% nrow() # 11

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1, visit_ends < last_day_fID) %>% nrow() # 5

visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1, visit_ends < last_day_fID) %>% nrow() # 11

@@

### No tie-breaking.
```{r}
Fig1_v2A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1_v2B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

@@

### Longest initiators only
```{r}
Fig1_v3A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1,
                                 initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

>>>>

clutch_status_guarding_summary_v2
```{r}
All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
# clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
# last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))

strats_data <- read_rds(here("saved_rds/strats_data.rds"))
```

@@

# 2 - When were females visited on their first clutch?
First I need to know when females were visited on their first clutch.
I also need to estimate the hatch date for clutches that never hatched so I can still show and run stats for relative desertion date. I do this by adding 20 days to the initiation date. The mean interval from initiation to hatch is 20 days.
```{r}
## Moved to Publilia-01-qc.Rmd
# visited_1st_4d_data <- strats_data %>%
#   group_by(location) %>%
#     mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
#   ungroup() %>%
#   mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
#                                       "Visited", "Not visited"),
#          ants = ifelse(ants_removed, "Ants removed", "Control"),
#          est_hatch = as_date(ifelse(is.na(hatch_date),
#                                  initiation_date + 20,
#                                  hatch_date)),
#          est_rel2h = visit_ends-est_hatch)

@@

I also need to know how to pick just one initiator when two (or more) females are present on a clutch on the first day eggs are observed.
```{r}
## Moved to Publilia-01-qc.Rmd
# visited_1st_4d_data_tb <- visited_1st_4d_data %>%
#   # 1) Longest initiator
#   mutate(initL = init_first_dur_rank == 1) %>% 
#   # 2) Shortest initiator
#   #  i) break ties by picking marked females over unmarked
#   group_by(location, init_first_dur_shortest) %>% 
#     mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
#   ungroup() %>%
#   #  ii) finally picking at random (only one case, identical predictor vars)
#   group_by(location, init_first_dur_shortest, initS_tmp) %>%
#     mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
#   ungroup()
```

@@

## 3.1 - Ant counts on plant; some ants_removed clutches were visited by ants, and vice versa
```{r}
## Moved to Publilia-01-qc.Rmd
# ant_counts <- All_data_v6 %>%
#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
#   filter(!is.na(initiation_date)) %>%
#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
#   group_by(location) %>%
#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
#            afh=Date>=est_hatch) %>%
#     summarize(ants_removed=first(ants_removed),
#               females_removed=first(females_removed),
#               n_antsP=sum(ants_P,na.rm=T),
#               ever_antsP=n_antsP>0,
#               mean_antsP=mean(ants_P,na.rm=T),
#               med_antsP=median(ants_P,na.rm=T),
#               
#               n_antsP_b4h=sum(ants_P&b4h),
#               ever_antsP_b4h=n_antsP_b4h>0,
#               mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
#               med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),
#               
#               n_antsP_afh=sum(ants_P&afh),
#               ever_antsP_afh=n_antsP_afh>0,
#               mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
#               med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
#   ungroup() %>%
#   mutate(Dorm=substr(location,1,1),
#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

@@

## 3.2 - Ant arrival times
```{r}
## Moved to Publilia-01-qc.Rmd
# antP_arrival_afh_data <- All_data_v6 %>%
#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
#   filter(!is.na(initiation_date)) %>%
#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
#   group_by(location) %>%
#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
#            afh=Date>=est_hatch,
#            is_antsP_afh=ants_P&afh) %>%
#     filter(is_antsP_afh) %>%
#     slice_head(n=1) %>% 
#   mutate(antP_arrival_afh=Date-est_hatch) %>%
#   select(location, antP_arrival_afh, ants_removed, females_removed,
#          initiation_date, est_hatch) %>%
#   ungroup() %>%
#   mutate(Dorm=substr(location,1,1),
#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
# 
# antP_last_b4h_data <- All_data_v6 %>%
#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
#   filter(!is.na(initiation_date)) %>%
#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
#   group_by(location) %>%
#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
#            afh=Date>=est_hatch,
#            is_antsP_bfh=ants_P&b4h) %>%
#     filter(is_antsP_bfh) %>%
#     slice_tail(n=1) %>% 
#   mutate(antP_last_b4h=Date-est_hatch) %>%
#   select(location, antP_last_b4h, ants_removed, females_removed,
#          initiation_date, est_hatch) %>%
#   ungroup() %>%
#   mutate(Dorm=substr(location,1,1),
#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
# 
# antL_arrival_afh_data <- All_data_v6 %>%
#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
#   filter(!is.na(initiation_date)) %>%
#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
#   group_by(location) %>%
#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
#            afh=Date>=est_hatch,
#            is_antsL_afh=ants_L&afh) %>%
#     filter(is_antsL_afh) %>%
#     slice_head(n=1) %>% 
#   mutate(antL_arrival_afh=Date-est_hatch) %>%
#   select(location, antL_arrival_afh, ants_removed, females_removed,
#          initiation_date, est_hatch) %>%
#   ungroup() %>%
#   mutate(Dorm=substr(location,1,1),
#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
# 
# antL_last_b4h_data <- All_data_v6 %>%
#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
#   filter(!is.na(initiation_date)) %>%
#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
#   group_by(location) %>%
#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
#            afh=Date>=est_hatch,
#            is_antsL_bfh=ants_L&b4h) %>%
#     filter(is_antsL_bfh) %>%
#     slice_tail(n=1) %>% 
#   mutate(antL_last_b4h=Date-est_hatch) %>%
#   select(location, antL_last_b4h, ants_removed, females_removed,
#          initiation_date, est_hatch) %>%
#   ungroup() %>%
#   mutate(Dorm=substr(location,1,1),
#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
# 
# ant_data <- ant_counts %>%
#   left_join(antP_last_b4h_data) %>%
#   left_join(antP_arrival_afh_data) %>%
#   left_join(antL_last_b4h_data) %>%
#   left_join(antL_arrival_afh_data)
# 
# visited_1st_4d_data_ants <- visited_1st_4d_data %>%
#   left_join(ant_data)

strats_data %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_last_b4h, color=females_removed)) +
  geom_point() +
  geom_abline(slope=1)

strats_data %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_arrival_afh, color=females_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  geom_abline(slope=1)

strats_data %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_last_b4h)) +
  geom_boxplot()

strats_data %>%
  filter(ants=="Control") %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)

strats_data %>%
  filter(ants=="Control", !females_removed) %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)
```

@@

### Not visited early
```{r}
## Not visited early
# ever ants b4h
ggplot(data = filter(strats_data, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(strats_data, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)
```

### Visited early
```{r}
# ever ants b4h
ggplot(data = filter(strats_data,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(strats_data,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)
```

@@

## 4.3 - Dealing with non-independence of multi-initiators: Using only longest or shortest initiator
Sample sizes
```{r}
# Samples sizes for "not visited" are the same across longests and shortests
filter(strats_data, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL) %>% nrow()

filter(strats_data, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initS) %>% nrow()

# Shortests have more females than longests for some reason??
filter(strats_data, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL) %>% nrow()

filter(strats_data, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initS) %>% nrow()

strats_data %>% filter(initL, mom_at_init, num_at_init>1) %>% nrow() # 34
strats_data %>% filter(initS, mom_at_init, num_at_init>1) %>% nrow() # 36

strats_data %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed) %>% nrow() # 13

strats_data %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed) %>% nrow() # 12

strats_data %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1) %>% nrow() # 12

strats_data %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1) %>% nrow() # 11

strats_data %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1, visit_ends < last_day_fID) %>% nrow() # 5

strats_data %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1, visit_ends < last_day_fID) %>% nrow() # 11

@@

### No tie-breaking.
```{r}
Fig1_v2A <- ggplot(data = filter(strats_data, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1_v2B <- ggplot(data = filter(strats_data, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

@@

### Longest initiators only
```{r}
Fig1_v3A <- ggplot(data = filter(strats_data, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1,
                                 initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1_v3B <- ggplot(data = filter(strats_data, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1,
                                 initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))
